---
title: "Draft Quarto document"
author: "Katrine Bovién Gørlitz"
format: html
---

## Header 1

```{r setup}
library(tidyverse)
library(here)
library(snakecase)
#| include: false
```

##Importing new data 
# Find function: Ctrl + shift + p
#New code block: Ctrl + ALt + i
#New pipe: Cmd + shift m 
#This data is written in pascal case (CollectionDatetime), we change it to snake case, which is where all words are written in lower case with words devided by a lowercase (and we therefore we added "library(snakecase)" in the code chunk above, and ", name_repair = to_snake_case)
#Insert "Help" section by inserting "?read_csv" in the console. You just use it when you need help, and it therefore should not be a part 
# To get an overview of just a bit of the data, we typed in "n_max = 100", which provides a tibble with max 100 rows
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

##Importing new data by myself without n_max
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
  )
```


##Importing new data by myself with n_max
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```
##Writing codes that can be used import more than one data set, at the time 
#name <- function(argument1, argument2) {
  # body of function
  output <- ...
  return(output)
}
```{r}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here
#'
#' @returns The sum of two numbers
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```
